Cybersecurity Is Too Important To Be Left To The Specialists

### 2019-01-16 ITiCSE2019.tex
Removed pagebreak
Added recomendations to abstract
Further tweaks to abstract

\def\IntroYear{2014}  % when BCS started asking for CyberSecurity
\begin{abstract}
There are numerous facets to cybersecurity education, from theory to practice, hardware and software, social and technical, to various other dimensions. Whilst various model curricula and associated recommendations exist, in this paper we address the questions ``what should the generalist computer scientist know'' and ``how well is that being taught''.  (Cyber)security -- if thought about at all -- has historically been left to specialists, frequently viewed as a masters level discipline or left to professional practice, sometimes called ``information assurance'', which worked, even if not well, in a waterfall model.  We have seen Agile and DevOps changing software and systems devleopment, but not necessarily the view of security; however, over recent years, there has been a recogition of the need for change, exemplified by the emergence of ``DevSecOps''. If security is not to be left to the experts, then the generalist must know about it. In the context of significant international computer science curriculum reform -- both in compulsory, as well as post-compulsory education -- what does this trend more generally for computer science and informatics education, and how we teach it?

In this paper, we frame a key social and global challenge in computing education by analysing the UK perspective on cybersecurity education, with a substantial national security, economic, and skills policy context, shaping the practical considerations for education professionals from schools through to universities. Through this analysis of policy and practice in the UK, we make a number of recommendations for future cybersecurity educational initiatives, with potential adoption and adaption in other jurisdictions.

@@

Specialist curricula abound: a recent one is \cite{ACMIEEEAISSIGSECIFIP}. However, given the shortage of specialists, in practice a good generalist with some CyberSecurity expertise can often get a ``specialist'' job.
\subsection{Research Questions}
\begin{enumerate}
\item The person in the street --- probably not. ({\emph{interesting point from a public engagement/science communication perspective -- aren't ``we'' trying to create a digitally competent and capable citizenry? Minor point but maybe worth mentioning e.g. being safe online, accessing public services, etc}})
\item[JHD]This is important, agreed, but I think this is being a user: think car driving rather than car design. BUT the point I heard from the WC Engineers ``how can security be an option --- safety certainly isn't'' is also relevant.
\item The general CS graduate.
\item The general CS masters graduate.
\item The specialist CS graduate.
\item The specialist CS masters graduate.
\end{enumerate}
\pagebreak
\section{Policy Context}

>>>>

\def\IntroYear{2014}  % when BCS started asking for CyberSecurity

\begin{abstract}
There are numerous facets to cybersecurity education, from theory to practice, hardware and software, to social and technical (as well as other important dimensions). Whilst various model curricula and associated recommendations have been presented and discussed in recent years, in this paper we attempt to address the questions ``what should the generalist computer scientist know'' and ``how well is that being taught''.  (Cyber)security -- if thought about at all -- has historically been left to specialists, frequently viewed as a masters level discipline or left to develop in professional practice, sometimes called ``information assurance'' in the UK and Europe, which worked, even if not well, in a waterfall model.

In the world of software and systems development, we have seen the disruption of Agile and DevOps, but not necessarily through the lens of security; however, more recently there has been a recogition of the need for change, exemplified by the emergence of ``DevSecOps''. If security is not to be left to the experts, then the generalist must know about it. Thus, in the context of widespread international computer science curriculum reform -- both in compulsory, as well as post-compulsory education -- what does this trend mean more generally for institutions and educators, and how do we teach it?

In this paper, we frame a key social and global challenge in computing education by analysing the UK perspective on cybersecurity education, with a substantial national security, economic, and skills policy context, shaping the practical considerations for education professionals from schools through to universities. Through this analysis of policy and practice in the UK, we make a number of recommendations for future cybersecurity educational initiatives, including practical suggestions for educators and curriculum designers, with a view for potential adoption and adaption in other jurisdictions.

We also make some

@@

Specialist curricula abound: a recent one is \cite{ACMIEEEAISSIGSECIFIP}. However, given the shortage of specialists, in practice a good generalist with some CyberSecurity expertise can often get a ``specialist'' job.
\subsection{Research Questions}
\begin{enumerate}
\item The person in the street --- probably not. ({\emph{interesting point from a public engagement/science communication perspective -- aren't ``we'' trying to create a digitally competent and capable citizenry? Minor point but maybe worth mentioning e.g. being safe online, accessing public services, etc}})
\item[JHD]This is important, agreed, but I think this is being a user: think car driving rather than car design. BUT the point I heard from the WC Engineers ``how can security be an option --- safety certainly isn't'' is also relevant.
\item The general CS graduate.
\item The general CS masters graduate.
\item The specialist CS graduate.
\item The specialist CS masters graduate.
\end{enumerate}
%\pagebreak - to fix URL issues
\section{Policy Context}
